---
title: Data Types
author: R Package Build
date: '2022-02-21'
slug: data-types
categories: []
tags: []
---

## Cat Lovers
# Call libraries
```{r}
library(tidyverse)
```

# Get data
```{r message=FALSE}
cat_lovers <- read_csv('https://raw.githubusercontent.com/thayerm/tidyverse/main/cat-lovers.csv')
```

## Summaries
# Incorrect Summary
```{r}
cat_lovers %>%
  summarise(mean_cats = mean(number_of_cats, na.rm = TRUE))
```

# Fixed Summaries
```{r}
glimpse(cat_lovers) #See what's happening with data

# Change number_of_cats from character to numeric data
cat_lovers %>%
  mutate(
    number_of_cats = case_when(
      name == "Ginger Clark" ~ "2",
      name == "Doug Bass"    ~ "3",
      TRUE                   ~ number_of_cats
      ),
    number_of_cats = as.numeric(number_of_cats)
    ) %>%
  summarise(mean_cats = mean(number_of_cats))

```
## Types of Data
```{r}
typeof(TRUE) #logical
typeof("hello") #character
typeof(1.43) #double
typeof(7) #double
typeof(7L) #integer - specified with L
typeof(1:3) #integer
```
# Concatenation
```{r}
# Create Vectors using concatentation
c(1, 2, 3)

c("Hello", "World!")

c(c("hi", "hello"), c("bye", "jello"))
```
## Converting Between Data Types {.tabset}
# With Intention
```{r}
x <- c(TRUE, FALSE)
x

typeof(x) # logical

y <- as.numeric(x)
y

typeof(y) # character
```
# Without Intention
```{r}
c(1, "Hello") # changes all values to character values
c(FALSE, 3L) # changes all to integer values
c(1.2, 3L) # all double values
c(2L, "two") # all character values
```

## Explicit vs. implicit coercion

 - Explicit coercion is when you call a function like as.logical(), as.numeric(), as.integer(), as.double(), or as.character()

 - Implicit coercion happens when you use a vector in a specific context that expects a certain type of vector

# Explicit Coercion
```{r}
x <- 1:3
typeof(x)
typeof(as.character(x)) # explicit
```


## Special Values
 - NA: Not available
 - NaN: Not a number
 - Inf: Positive infinity
 - -Inf: Negative infinity
```{r}
pi / 0 # Inf
0 / 0  # NaN
1/0 - 1/0 # NaN
1/0 + 1/0 # inf
```
# Nas

```{r}
x <- c(1, 2, 3, 4, NA)
mean(x)

mean(x, na.rm = TRUE)

summary(x)
```

```{r}
typeof(NA) # returns logical
```

```{r}
# Due to identity laws (NA is considered unknown could be true or false)
TRUE | NA # returns TRUE
FALSE | NA # returns NA
```

