---
title: Importing Data
author: R Package Build
date: '2022-02-23'
slug: importing-data
categories: []
tags: []
---
# Call packages
```{r warning=FALSE}
library(tidyverse)
library(readr)
library(readxl)
```


# Import Data
```{r warning=FALSE}
url <- "https://raw.githubusercontent.com/thayerm/tidyverse/main/nobel.csv"
nobel <- read_csv(url)
```

# Write data
## Data File
```{r}
df <- tribble(
  ~x, ~y,
  1,  "a",
  2,  "b",
  3,  "c"
)
write_csv(df, file = "data/df.csv")
# Read to inspect it
read_csv("data/df.csv")
```
# Naming variables
## Data w Bad Names
```{r}
edibnb_badnames <- read_csv("https://raw.githubusercontent.com/thayerm/tidyverse/main/edibnb-badnames.csv")
names(edibnb_badnames)
```
## Error from spaces in variable name
```{r}
#ggplot(edibnb_badnames, #aes(x = Number of #bathrooms, y = Price)) +
#  geom_point()
```
## To fix error - Define column names
```{r}
edibnb_col_names <- read_csv("https://raw.githubusercontent.com/thayerm/tidyverse/main/edibnb-badnames.csv",
                             col_names = c("id", "price", 
                                           "neighbourhood", "accommodates",
                                           "bathroom", "bedroom", 
                                           "bed", "review_scores_rating", 
                                           "n_reviews", "url"))
names(edibnb_col_names)
```
## Format text to snake case
```{r}
edibnb_clean_names <- read_csv("https://raw.githubusercontent.com/thayerm/tidyverse/main/edibnb-badnames.csv") %>%
  janitor::clean_names()
names(edibnb_clean_names)
```

# Variable types
```{r}
read_csv("https://raw.githubusercontent.com/thayerm/tidyverse/main/df-na.csv")
```
## Explicit NAs
```{r}
read_csv("https://raw.githubusercontent.com/thayerm/tidyverse/main/df-na.csv", 
         na = c("", "NA", ".", "9999", "Not applicable"))
# Set problem elements to na directly
```
## Specify Column Types
```{r}
read_csv("https://raw.githubusercontent.com/thayerm/tidyverse/main/df-na.csv", col_types = list(col_double(), 
                                            col_character(), 
                                            col_character()))
```
## Different Column Types
- col_character() -	character
- col_date() -	date
- col_datetime() -	POSIXct (date-time)
- col_double() -	double (numeric)
- col_factor() -	factor
- col_guess() -	let readr guess (default)
- col_integer() -	integer
- col_logical() -	logical
- col_number() -	numbers mixed with non-number characters
- col_numeric() -	double or integer
- col_skip() -	do not read
- col_time() -	time

# Case Study
## Get data
```{r}
fav_food <- read_excel("data/favourite-food.xlsx")
fav_food
```
## Variable Names
```{r}
fav_food <- read_excel("data/favourite-food.xlsx") %>%
  janitor::clean_names()
fav_food
```
# Deal With NAs
```{r}
fav_food <- read_excel("data/favourite-food.xlsx",
                       na = c("N/A", "99999")) %>%
  janitor::clean_names()
fav_food
```
## Change Age to Numeric
```{r}
fav_food <- fav_food %>%
  mutate(
    age = if_else(age == "five", "5", age),
    age = as.numeric(age)
    )
glimpse(fav_food)
```

## Sort by Socio-Economic Status
```{r}
fav_food %>%
  count(ses)
```
## Make SES a factor
```{r}
fav_food <- fav_food %>%
  mutate(ses = fct_relevel(ses, "Low", "Middle", "High"))
fav_food %>%
  count(ses)
```
## Putting it all together to create a better data frame
```{r}
fav_food <- read_excel("data/favourite-food.xlsx", na = c("N/A", "99999")) %>%
  janitor::clean_names() %>%
  mutate(
    age = if_else(age == "five", "5", age), 
    age = as.numeric(age),
    ses = fct_relevel(ses, "Low", "Middle", "High")
  )
fav_food
```
## Read and Write file as CSV
```{r}
write_csv(fav_food, file = "data/fav-food-clean.csv")
fav_food_clean <- read_csv("data/fav-food-clean.csv")
```
## Note SES is no longer a factor
```{r}
fav_food_clean %>%
  count(ses)
```
## Use write_rds and read_rds to preserve certain variable type info
```{r}
write_rds(fav_food, file = "data/fav-food-clean.rds")
fav_food_clean <- read_rds("data/fav-food-clean.rds")
fav_food_clean %>%
  count(ses)
```






