---
title: Regression Models
author: ''
date: '2022-03-26'
slug: regression-models
categories: []
tags: []
---
## The model predicts the price to be $2844.49 which makes the price of $3100 slightly high, but not a rip off (work below)

#Call Libraries
```{r}
library(tidyverse)
library(ISLR)
library(boot)
```

#Get Data and transform as necessary (make Wholesaler a factor)
```{r}
df <- read_csv("https://raw.githubusercontent.com/thayerm/mkthayer/main/content/post/2022-03-26-regression-models/data/Professor_Proposes_Data.csv")
df$Wholesaler <- as.factor(df$Wholesaler)
```

```{r}
## Set Seed: To reproduce the sampling for train - test split
set.seed(1)
head(df)
dim(df)
## Create an index to randomly sample 50% records for data set df
train <- sample(440,220)
head(train)
```


# Exploratory Data Analysis
```{r}
df %>%
  ggplot(aes(Price)) +
  geom_histogram()
df %>%
  ggplot(aes(Carat)) +
  geom_histogram()
summary(Price) 
```
Both Price And Carats have a bimodal distributions with a low and high price cluster and a small and large carat cluster

```{r}
attach(df)
#attach data frame
```

```{r}
table(Certification)

# Split into established and small labs
df[Certification == "GIA", "Certification"] <- "GIA/AGS"
df[Certification == "AGS", "Certification"] <- "GIA/AGS"
df[Certification == "DOW", "Certification"] <- "Rest"
df[Certification == "IGI", "Certification"] <- "Rest"
df[Certification == "EGL", "Certification"] <- "Rest"

table(df$Certification)
```
```{r}
table(Colour)

df[Colour == "D", "Colour"] <- "Colorless/Near Colorless"
df[Colour == "F", "Colour"] <- "Colorless/Near Colorless"
df[Colour == "E", "Colour"] <- "Colorless/Near Colorless"
df[Colour == "G", "Colour"] <- "Colorless/Near Colorless"
df[Colour == "H", "Colour"] <- "Colorless/Near Colorless"
df[Colour == "I", "Colour"] <- "Colorless/Near Colorless"
df[Colour == "J", "Colour"] <- "Faint to Very Light Yellow"
df[Colour == "K", "Colour"] <- "Faint to Very Light Yellow"
df[Colour == "L", "Colour"] <- "Faint to Very Light Yellow"

table(df$Colour)
```
```{r}
table(Cut)
# Even representation of data
```
```{r}
table(Clarity)

#Interval scaling
df[Clarity == "I1", "Clarity"] <- "1"
df[Clarity == "I2", "Clarity"] <- "2"
df[Clarity == "SI1", "Clarity"] <- "3"
df[Clarity == "SI2", "Clarity"] <- "4"
df[Clarity == "SI3", "Clarity"] <- "5"
df[Clarity == "VS1", "Clarity"] <- "6"
df[Clarity == "VS2", "Clarity"] <- "7"
df[Clarity == "VVS1", "Clarity"] <- "8"
df[Clarity == "VVS2", "Clarity"] <- "9"
df$Clarity <- as.numeric(df$Clarity)
table(df$Clarity)
```
```{r}
table(Polish)
df[Polish == "F", "Polish"] <- "Fair to Good"
df[Polish == "G", "Polish"] <- "Fair to Good"
df[Polish == "v", "Polish"] <- "Very Good to Ideal"
df[Polish == "V", "Polish"] <- "Very Good to Ideal"
df[Polish == "I", "Polish"] <- "Very Good to Ideal"
df[Polish == "X", "Polish"] <- "Very Good to Ideal"
table(df$Polish)
```
```{r}
table(Symmetry)
```
## Bivariate Analysis

```{r}
df %>%
  ggplot(aes(x=Carat,y=Price, color=Wholesaler)) +
  geom_point()
```
```{r}
df1 <- df %>%
  filter(Wholesaler == 3)

max(df1$Carat)
#The largest Carat used by the the third Wholesaler is just 0.3, since the professor wants a 0.9 Carat diamond, its better to focus on data from the 1st and 2nd wholesaler wehere he will have to buy from
```
```{r}
df23 <- df %>%
  filter(Wholesaler == 2 | Wholesaler == 1)
# Data set only looking at the 1st and second wholesaler
# dimensions on new df
dim(df23)

df23 %>%
  ggplot(aes(x=Carat,y=Price, color=Wholesaler)) +
  geom_point()
```

We can model both the data sets discovered in the bivariate analysis

## Regression
```{r}
Carat_Regression <- lm(Price ~ Carat, data = df23)
coef(Carat_Regression)
summary(Carat_Regression)
aov(Carat_Regression)

```
The R2 of just 10.72% suggest a very weak correlation, meaning carat alone can't explain the price. However, the low P-value suggests Carat is a significant value
```{r}
Clarity_Regression <- lm(Price ~ Clarity, data = df)
coef(Clarity_Regression)
summary(Clarity_Regression)
aov(Clarity_Regression)
```
The R2 is just 10.24% which shows low levels of correlation. However, the low p-score and high F-statistic suggests clarity is very significant in predicting price
```{r}
Certification_Regression <- lm(Price ~ Certification, data = df23)
coef(Certification_Regression)
summary(Certification_Regression)
aov(Certification_Regression)
```
Certification has a R2 of just 8.15% as well as a comparitively low F-statistic. The p-scores are still < .05 suggesting it is still significant
```{r}
Cut_Regression <- lm(Price ~ Cut, data = df23)
coef(Cut_Regression)
summary(Cut_Regression)
aov(Cut_Regression)
```
Cut has a R2 of 14.4%, which is one of the strongest correlations among the variables. The p scores are also in significant range
```{r}
Polish_Regression <- lm(Price ~ Polish, data = df23)
coef(Polish_Regression)
summary(Polish_Regression)
aov(Polish_Regression)
```
Polish has a R2 of 15.05%, which is the strongest correlation among the variables. The F-statistic is 8.291 which is on the lower end but the p-scores still fall in significant range.
```{r}
Symmetry_Regression <- lm(Price ~ Symmetry, data = df23)
coef(Symmetry_Regression)
summary(Symmetry_Regression)
aov(Symmetry_Regression)
```
The R2 is 14.09%. The p-scores are all significant or very significant
```{r}
Colour_Regression <- lm(Price ~ Colour, data = df23)
coef(Colour_Regression)
summary(Colour_Regression)
aov(Colour_Regression)
```
The colors with significant p-values are the yellow colors, whereas the colorless ones don't have a p < 0.05 in general. The R2 is 9.9% showing very little correlation and the F-statistic is also comparitively much lower than the rest.

```{r}
attach(df23)
```

### Multiple Linear Regression Model

```{r}
model <- glm(Price ~ Carat + Colour + Symmetry + Clarity + Cut + Polish + Certification, data = df23)
summary(model)
```
### Plugging in the values to the model(526.71 + 2224.79(.9) - 505.43 + 99.70 + 603.27 +36.13 + 90.59 + 6.29) you get the price for the diamond is $2859.29 with a 95% confidence interval of $2042.35 to $3676.23. Overall this is slightly lower than his expected price of $3100, however this doesn't account for the entire ring, just the diamond. The largest determinants of price was the Carat size and Clarity of the diamond.


