---
title: Regression Models
author: ''
date: '2022-03-26'
slug: regression-models
categories: []
tags: []
---
## The model predicts the price of the diamond as $2859.29 with a 95% confidence interval of $2042.35 to $3676.23. Overall this is slightly lower than his expected price of $3100, however this doesn't account for the entire ring, just the diamond. (work below)

#Call Libraries
```{r}
library(tidyverse)
library(ISLR)
library(boot)
```

#Get Data and transform as necessary (make Wholesaler a factor)
```{r}
df <- read_csv("https://raw.githubusercontent.com/thayerm/mkthayer/main/content/post/2022-03-26-regression-models/data/Professor_Proposes_Data.csv")
df$Wholesaler <- as.factor(df$Wholesaler)
```

```{r}
## Set Seed: To reproduce the sampling for train - test split
set.seed(1)
head(df)
dim(df)
## Create an index to randomly sample 50% records for data set df
train <- sample(440,220)
head(train)
```

```{r}
attach(df)
#attach data frame
```

```{r, echo = FALSE, message=FALSE,results='hide'}
as.factor(Certification)
as.factor(Colour)
as.factor(Cut)
as.factor(Clarity)
as.factor(Polish)
as.factor(Symmetry)
```

# Exploratory Data Analysis
```{r}
df %>%
  ggplot(aes(Price)) +
  geom_histogram()
df %>%
  ggplot(aes(Carat)) +
  geom_histogram()

```
Both Price And Carats have a bimodal distributions with a low and high price cluster and a small and large carat cluster



```{r}
table(Certification)

# Split into established and small labs
levels(Certification)
levels(Certification) <- list("GIA/AGS" = c("GIA","AGS"),
                              "Rest" = c("DOW", "IGI","EGL"))

table(df$Certification)
```
```{r}
table(Colour)
levels(Colour) <- list("Colorless" = c("D","F","E","G","H","I"),
                              "Yellow" = c("J", "K","L"))

table(df$Colour)
```
```{r}
table(Cut)
# Even representation of data
levels(Cut) <- list("Fair" = "F",
                              "Good" = "G",
                              "Ideal" = "I",
                              "Very Good" = "V",
                              "Excellent" = "X")
levels(Cut)
```
```{r}
table(Clarity)
```
```{r}
table(Polish)
levels(Cut) <- list("Fair to Good" = c("F", "G"),
                    "Very Good to Ideal" = c("I","V", "X"))
```
```{r}
table(Symmetry)
levels(Symmetry) <- list("Fair" = "F",
                              "Good" = "G",
                              "Ideal" = "I",
                              "Very Good" = "V",
                              "Excellent" = "X")
```
## Bivariate Analysis

```{r}
df %>%
  ggplot(aes(x=Carat,y=Price, color=Wholesaler)) +
  geom_point()
```
```{r}
df1 <- df %>%
  filter(Wholesaler == 3)

max(df1$Carat)
#The largest Carat used by the the third Wholesaler is just 0.3, since the professor wants a 0.9 Carat diamond, its better to focus on data from the 1st and 2nd wholesaler wehere he will have to buy from
```
```{r}
df23 <- df %>%
  filter(Wholesaler == 2 | Wholesaler == 1)
# Data set only looking at the 1st and second wholesaler
# dimensions on new df
dim(df23)

df23 %>%
  ggplot(aes(x=Carat,y=Price, color=Wholesaler)) +
  geom_point()
```

We can model both the data sets discovered in the bivariate analysis

## Regression
```{r}
Carat_Regression <- lm(Price ~ Carat, data = df23)
coef(Carat_Regression)
summary(Carat_Regression)
aov(Carat_Regression)

```
The R2 of just 10.72% suggest a very weak correlation, meaning carat alone can't explain the price. However, the low P-value suggests Carat is a significant value
```{r}
Clarity_Regression <- lm(Price ~ Clarity, data = df)
coef(Clarity_Regression)
summary(Clarity_Regression)
aov(Clarity_Regression)
```
The R2 is just 10.24% which shows low levels of correlation. However, the low p-score and high F-statistic suggests clarity is very significant in predicting price
```{r}
Certification_Regression <- lm(Price ~ Certification, data = df23)
coef(Certification_Regression)
summary(Certification_Regression)
aov(Certification_Regression)
```
Certification has a R2 of just 8.15% as well as a comparitively low F-statistic. The p-scores are still < .05 suggesting it is still significant
```{r}
Cut_Regression <- lm(Price ~ Cut, data = df23)
coef(Cut_Regression)
summary(Cut_Regression)
aov(Cut_Regression)
```
Cut has a R2 of 14.4%, which is one of the strongest correlations among the variables. The p scores are also in significant range
```{r}
Polish_Regression <- lm(Price ~ Polish, data = df23)
coef(Polish_Regression)
summary(Polish_Regression)
aov(Polish_Regression)
```
Polish has a R2 of 15.05%, which is the strongest correlation among the variables. The F-statistic is 8.291 which is on the lower end but the p-scores still fall in significant range.
```{r}
Symmetry_Regression <- lm(Price ~ Symmetry, data = df23)
coef(Symmetry_Regression)
summary(Symmetry_Regression)
aov(Symmetry_Regression)
```
The R2 is 14.09%. The p-scores are all significant or very significant
```{r}
Colour_Regression <- lm(Price ~ Colour, data = df23)
coef(Colour_Regression)
summary(Colour_Regression)
aov(Colour_Regression)
```
The colors with significant p-values are the yellow colors, whereas the colorless ones don't have a p < 0.05 in general. The R2 is 9.9% showing very little correlation and the F-statistic is also comparitively much lower than the rest.

```{r}
attach(df23)
```

### Multiple Linear Regression Model

```{r}
model <- glm(Price ~ Carat + Colour + Symmetry + Clarity + Cut + Polish + Certification, data = df23)
summary(model)
```
### Plugging in the values to the model(526.71 + 2224.79(.9) - 505.43 + 99.70 + 603.27 +36.13 + 90.59 + 6.29) you get the price for the diamond is $2859.29 with a 95% confidence interval of $2042.35 to $3676.23. Overall this is slightly lower than his expected price of $3100, however this doesn't account for the entire ring, just the diamond. The largest determinants of price was the Carat size and Clarity of the diamond.


